%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------

  \cventry
    {Embedded Systems Engineer / Lead Electrical Engineer} % Job title
    {ColdQuanta, Inc} % Organization
    {Boulder, CO} % Location
    {November 2019 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
		\item {
			Leads electrical engineering team for quantum computing project.
		}
        \item {
			Develops high-performance distributed real-time systems utilizing \textrm{Xilinx} FPGAs with both soft (\textrm{OpenRISC}/\textrm{RISC-V}) and hard (\textrm{ARMv7}) processors.
        }
		\item {
			Develops software-defined radio applications in \textrm{C++}, \textrm{Python}, and \textrm{Verilog}.
		}
        \item {
			Develops distributed health and monitoring interfaces.
        }
		\item {
			Architected integrated electronics platform for next-generation NASA Cold Atom Laboratory.
		}
		\item {
				Developed high-speed PXIe control hardware (\textrm{Orcad/Allegro}) and firmware (\textrm{C}/\textrm{Rust}) platform for real-time quantum physics experiments.
		}
      \end{cvitems}
    }

%---------------------------------------------------------

  \cventry
    {Embedded Systems Engineer} % Job title
    {AQRONOS, Inc} % Organization
    {Thornton, CO} % Location
    {May 2019 - November 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {
			Led embedded system and electrical engineering U.S. R\&D Team.
        }
        \item {
			Researched novel high-speed frequency space data acquisition techniques for FMCW Lidar. Developed electro-optical modulation and RF acquisition systems.
        }
        \item {
			Developed beam-steering controller system synchronizing galvo and BLDC motors.
        }
		\item {
			Developed embedded Linux and FPGA digital systems.
		}
		\item {
			Developed firmware and HDL for LIDAR controllers and supported software developers.
		}
		\item {
			Developed embedded Linux, FPGA, and electrical systems for LIDAR Time-Of-Flight prototype.
		}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Embedded Systems Engineer} % Job title
    {RMI Laser, LLC} % Organization
    {Lafayette, CO} % Location
    {May 2015 - May 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {
            Researched and developed embedded Linux and FPGA framework for high-speed
            marking lasers (fiber and DPSS) with a focus on high
			\linebreak
			throughput and repeatibility as well as compatibility with modern IoT/automation infrastructures.
        }
        \item {
            Successfully brought laser prototype into production and to market with many
            units deployed in the field.
        }
        \item {
            Interfaced vision systems and motion control systems with laser systems.
        }
        \item {
            Worked closely with Senior Electrical Engineer to develop prototype hardware
            and resolve issues across board revisions.
        }
        \item {
            Developed laser drivers for legacy products from scratch for Linux and later
            ported to Android (with $Java$ interface).
        }
        \item {
            Developed embedded Linux system to adapt legacy units to be compatible with
            advanced manufacturing systems and modern hardware. Several prominent
            companies depend on this device to flexibly scale manufacturing operations
            across the world.
        }
        \item {
            Engineered electrical systems for custom automated applications.
        }
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
